Higher-Order unification for free!

### 2024-07-01 paper/main.tex
ensures the mapping are bijective" are => is

\noindent
When a single \elpiIn{ovariable} occurs multiple times with different numbers
of arguments, the compiler generates multiple mappings for it, on a first
approximation, and then ensures the mapping are bijective by introducing
\linketa; this detail is discussed in section \ref{sec:invariant1}.

>>>>

\noindent
When a single \elpiIn{ovariable} occurs multiple times with different numbers
of arguments, the compiler generates multiple mappings for it, on a first
approximation, and then ensures the mapping is bijective by introducing
\linketa; this detail is discussed in section \ref{sec:invariant1}.
